Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-05-25 mu/article/article.tex
Made calv.kk* and calv.sm_0.03* for 0-360 deg for up and alt structures

The spin density injection current $\dot{K}^{\mathrm{ab}}$ can be written in
terms of a material response pseudotensor $\mu^{\mathrm{abcd}}(\omega)$ as
% with speed along direction $\mathrm{a}$ and spin
% polarization along $\mathrm{b}$ is defined as
\begin{equation*}
\dot{K}^{\mathrm{ab}}(\omega) = \mu^{\mathrm{abcd}}(\omega)
E^{\mathrm{c}}(\omega) E^{\mathrm{d*}}(\omega)
\label{eq:dotk}
\end{equation*}
where the roman superscripts denote Cartesian components corresponding
$\mathrm{a}$ to the spin velocity direction and $\mathrm{b}$ to the spin
polarization direction and the pseudotensor can be written as
\begin{widetext}
\begin{align}
\mu^{\mathrm{abcd}} (\omega) 
&=
\frac{\pi e^{2}}{\hbar^{2}} \int 
\frac{d^{3}K}{8 \pi^{3}}
\sum_{vcc'}^{'}
\mathrm{Re} \left[ K^{\mathrm{ab}}_{cc'} 
\left( 
r^{\mathrm{c}}_{vc'} 
r^{\mathrm{d}}_{cv } +
(c \leftrightarrow d)
\right) 
\right]
\delta(\omega-\omega_{cv})
\label{eq:mu}
% \\
% K^{\mathrm{ab}}_{mn}
% &=
% \sum_{\ell}v^{\mathrm{a}}_{nl} S^{\mathrm{b}}_{lm}
% \label{eq:velspi-matelem}
\end{align}
\end{widetext}
where $K^{\mathrm{ab}}_{mn}(\mathbf{k}) =
\sum_{\ell}v^{\mathrm{a}}_{nl}(\mathbf{k}) S^{\mathrm{b}}_{lm}(\mathbf{k})$ are
the spin current matrix elements that, using time reversal invariance,
$K^{\mathrm{ab}}_{nm}(\mathbf{-k}) = K^{\mathrm{ab*}}(\mathbf{k}) $. The $'$ in
the sum means that $c$ and $c'$ are quasi degenerate states and the sum only
covers these states and since $mu$ is real we have that
$\mu^{\mathrm{abcd}}(\omega) = \mu^{\mathrm{abdc}}(\omega)$.

Now we define the spin velocity, $\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ as
the speed at which the spin polarized in the $\mathrm{b}$   direction moves
along the $\mathrm{a}$ direction when a normal incident beam reaches the $xy$
plane with a polarization angle $\alpha$. Then,
\begin{widetext}
\begin{align}
\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha) + 
2\mu^{\mathrm{abxy}}(\omega)
E^{2}(\omega)\cos(\alpha)\sin(\alpha)}
{\xi^{\mathrm{xx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha)},
\nonumber \\
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)\sin^{2}(\alpha) + 
\mu^{\mathrm{abxy}}(\omega)\sin(2\alpha)}
{\xi^{\mathrm{xx}}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)\sin^{2}(\alpha)},
\label{eq:vab}
\end{align}
\end{widetext}
where $\xi^{\mathrm{aa}}(\omega)$ are the carrier generation rate tensor
components\cite{arzatePRB14}.
% 
For an angle $\alpha = \frac{\pi}{4}$ this expression can be reduced to 
\begin{align}
\mathcal{V}^{\mathrm{ab}} (\omega)
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega) + \mu^{\mathrm{abyy}}(\omega) + 
2\mu^{\mathrm{abxy}}(\omega)}
{\xi^{\mathrm{xx}}(\omega) + \xi^{\mathrm{yy}}(\omega)}.
\label{eq:vab-90deg}
\end{align}

@@

\subsection{Fixing spin}\label{sec:theory-fixspin}
Considering that we have 2D structures, one of the options is fix the spin along
the $x$, $y$, or $z$ Cartesian coordinates. We define the magnitude of the spin
velocity with spin polarization along the $\mathrm{b}$ direction as 
\begin{align}
|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)| 
&=
\sqrt{
[\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)]^{2}\ +
[\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)]^{2}\ 
}, 
\label{eq:vs-mag}
\end{align}
and the angle at which the spin velocity is directed on the $xy$ plane as
\begin{align}
\gamma_{\mathrm{b}} (\omega,\alpha)
&=
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)}
{\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)} \right),
\label{eq:gamma-ang}
\end{align}
where the angle is measured in the counter-clockwise direction from the positive
$x$ Cartesian coordinate. We also define two special angles
\begin{align}
\gamma_{\mathrm{b \parallel}}(\omega,\alpha) &= \alpha, 
\label{eq:gammapar} 
\\
\gamma_{\mathrm{b \perp}}(\omega,\alpha) &= \alpha \pm 90^{\circ}.
\label{eq:gammaperp}
\end{align}
The first corresponds to the case when the spin velocity is directed, on the
$xy$ plane in the same direction of the polarization angle of the incoming beam;
the second one corresponds to the case when the spin velocity is directed
perpendicularly respect to the polarization angle of the incoming beam.

@@

In a similar way we can fix the velocity on the $xy$ plane along $x$ or $y$
Cartesian coordinate and then define the magnitude of the spin velocity directed
along the $\mathrm{a}$ direction as
\begin{align}
|\mathcal{V}^{\mathrm{a}}&(\omega,\alpha)| = \nonumber \\
&\sqrt { 
[\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)]^{2} +
[\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)]^{2} +
[\mathcal{V}^{\mathrm{az}}(\omega,\alpha)]^{2} .
},
\label{eq:vv-mag}
\end{align}
Then, the spin direction depends of the components of the previous equation and
so we define the spin orientation polar and azimuthal angles as
\begin{align}
\theta_{\mathrm{a}}  (\omega,\alpha)
=& 
\cos^{-1} \left( \frac{\mathcal{V}^{\mathrm{az}}(\omega,\alpha)}
{|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|} \right),
& 0 \leq &\theta \leq \pi, 
\label{eq:polar-ang}
\\
\varphi_{\mathrm{a}} (\omega,\alpha)
=& 
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)}
{\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)} \right),
& 0 \leq &\varphi \leq 2\pi.
\label{eq:azimuthal-ang} 
\end{align}
where $\theta_{\mathrm{a}}(\omega,\alpha)$ is measured from the positive to the
negative $z$ Cartesian coordinate and $\varphi_{\mathrm{a}}(\omega,\alpha)$ is
measured on the $xy$ plane in the counter-clockwise direction from the positive
$x$ Cartesian coordinate.

@@

Using the Eq. \eqref{eq:vs-mag}, we calculated the
$|\mathcal{V}_{\sigma^{\mathrm{b}}}|(\omega,\alpha)$ response and made the
analysis for the case when the spin is fixed in the $z$ direction, directed
perpendicularly to the surface of the \emph{alt} and \emph{up} structures. Also,
using the Eq. \eqref{eq:gamma-ang}, we determined the angle
$\gamma_{\mathrm{b}}(\omega,\alpha)$ where the spin-velocity is directed on the
surface of the each structure.

@@

The most interesting case is that for which the spin is perpendicular to the
surface corresponding to $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$.

@@

For this case we first analyzed two energy ranges for the \emph{up} structure,
the first for an incoming energy beam from 0.0\,eV to 0.2\,eV which include the
THz and the Mid Infrared (MIR) range, where the absolute maximum of the

@@

for which value the response is maximized for the \emph{up} structure. In the

@@

from evaluate Eq. \eqref{eq:gamma-ang}, and in the bottom frames the
panels we present the corresponding components
$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ and
$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$. Also we present two circled and

@@

parallel (Eq. \ref{eq:gammapar}) and perpendicular (Eq. \ref{eq:gammaperp}) and
the arrows are directed to the value of the response corresponding to those

@@

and the response direction angle are collinear (Eq. \ref{eq:gammapar}) being

@@

For the \emph{alt} structure we analyzed the energy range for the incident beam
from 0.6\,eV to 1.0\,eV, corresponding to the NIR radiation, where the absolute
maximum of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response is
obtained.
% 
In Fig. \ref{fig:alt-3d-vsb} we present the
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ spectra for the \emph{alt}
structure.
% 
% From this figure we found that the zone where the absolute maximum response is
% held corresponds to a energy range from 0.90\,eV to 0.93\,eV and polarization
% angles $\alpha$ between $120^{\circ}$ and $150^{\circ}$. Also, a local maximum
% is obtained for the same polarization angles but for energies between 0.67\,eV
% and 0.75\,eV.
% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of ALT |V_{s^z}| & gamma  vs. alpha agle
% %%%%%%%%%%%%%%%%%
% 
From Figs. \ref{fig:alt-3d-vsb} and \ref{fig:alt-vaz-rag} we have that the
absolute maximum response is obtained for an incoming beam with polarization
angle $\alpha=145^{\circ}$ reaching a velocity of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 43.0$\,Km/s for the spin
polarized in the $\mathrm{z}$ direction and resulting in a velocity angle
$\gamma_{\mathrm{z}}(\omega,\alpha)=50^{\circ}$ on the first Cartesian Quadrant
of the $xy$ plane.
% 
Also, from the top frame of Fig. \ref{fig:alt-vaz-rag} we found that the
velocity angle has small variations being centered at $51.5^{\circ}$ and having
variations of $\pm 2^{\circ}$ for the polarization angle range $0^{\circ} \leq
\alpha \leq 180^{\circ}$.
% 
Again the circled box indicates the collinear angle (Eq.
\eqref{eq:gammapar}) corresponding to
$\gamma_{\mathrm{z}\parallel}(\omega,\alpha) = 53.5^{\circ}$ corresponding a
value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 12.7$\,Km/s; the
blue square box indicates the perpendicular angles corresponding values
$\alpha=140^{\circ}$ and $\gamma_{\mathrm{z}\perp}(\omega,\alpha)=50^{\circ}$
with a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=43$\,Km/s.
% 
Again, for the cases in which the spin polarization is parallel to the surface
of the \emph{alt} structure was calculated but the plots are not presented here.
The absolute maxima for the case when the spin polarization is directed in the
$\mathrm{x}$ and $\mathrm{y}$ direction are obtained for an energy of the
incoming beam equal to 0.912\,eV and polarization angle $\alpha=145^{\circ}$
resulting in values of
$|\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)|=27.1$\,Km/s and
$|\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha)|=33.2$\,Km/s.

>>>>

The spin density injection current $\dot{K}^{\mathrm{ab}}(\omega)$, where the
roman superscripts denote Cartesian components corresponding $\mathrm{a}$ to the
spin velocity direction and $\mathrm{b}$ to the spin polarization direction, can
be written in terms of a material response pseudotensor
$\mu^{\mathrm{abcd}}(\omega)$ as
\begin{equation*}
\dot{K}^{\mathrm{ab}}(\omega) = \mu^{\mathrm{abcd}}(\omega)
E^{\mathrm{c}}(\omega) E^{\mathrm{d*}}(\omega)
\label{eq:dotk}
\end{equation*}
where the pseudotensor is given by\cite{bhatPRL05}
\begin{widetext}
\begin{align}
\mu^{\mathrm{abcd}} (\omega) 
&=
\frac{\pi e^{2}}{\hbar^{2}} \int 
\frac{d^{3}K}{8 \pi^{3}}
\sum_{vcc'}^{'}
\mathrm{Re} \left[ K^{\mathrm{ab}}_{cc'} 
\left( 
r^{\mathrm{c}}_{vc'} 
r^{\mathrm{d}}_{cv } +
(c \leftrightarrow d)
\right) 
\right]
\delta(\omega-\omega_{cv})
\label{eq:mu}
\end{align}
\end{widetext}
where $K^{\mathrm{ab}}_{mn}(\mathbf{k}) =
\sum_{\ell}v^{\mathrm{a}}_{nl}(\mathbf{k}) S^{\mathrm{b}}_{lm}(\mathbf{k})$ are
the spin current matrix elements that, using time reversal invariance, satisfy
the relation $K^{\mathrm{ab}}_{nm}(\mathbf{-k}) = K^{\mathrm{ab*}}(\mathbf{k})
$. The $'$ in the sum means that $c$ and $c'$ are quasi degenerate states and
the sum only covers these states and since $\mu$ is real we have that
$\mu^{\mathrm{abcd}}(\omega) = \mu^{\mathrm{abdc}}(\omega)$.

Now we define the spin velocity, $\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ as
the speed at which the spin polarized in the $\mathrm{b}$   direction moves
along the $\mathrm{a}$ direction when a normal incident beam reaches the $xy$
plane with a polarization angle $\alpha$ as
\begin{widetext}
\begin{align}
\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha) + 
2\mu^{\mathrm{abxy}}(\omega)
E^{2}(\omega)\cos(\alpha)\sin(\alpha)}
{\xi^{\mathrm{xx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha)},
\nonumber \\
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)\sin^{2}(\alpha) + 
\mu^{\mathrm{abxy}}(\omega)\sin(2\alpha)}
{\xi^{\mathrm{xx}}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)\sin^{2}(\alpha)},
\label{eq:vab}
\end{align}
\end{widetext}
where $\xi^{\mathrm{aa}}(\omega)$ are the carrier generation rate tensor
components\cite{arzatePRB14}.
% 
For an angle $\alpha = \frac{\pi}{4}$ this expression can be reduced to 
\begin{equation*}\label{eq:vab-90deg}
\mathcal{V}^{\mathrm{ab}} (\omega)
= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega) + \mu^{\mathrm{abyy}}(\omega) + 
2\mu^{\mathrm{abxy}}(\omega)}
{\xi^{\mathrm{xx}}(\omega) + \xi^{\mathrm{yy}}(\omega)}.
\end{equation*}

@@

\subsection{Fixing spin}\label{sec:theory-fixspin}

Considering that we have 2D structures, one of the options to analyze the spin
velocity (Eq. \eqref{eq:vab}) is fixing the spin along the $x$, $y$, or $z$
Cartesian coordinates. We define the magnitude of the spin velocity with spin
polarization along the $\mathrm{b}$ direction as
\begin{align}
|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)| 
&=
\sqrt{
[\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)]^{2}\ +
[\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)]^{2}\ 
}, 
\label{eq:vs-mag}
\end{align}
and the angle at which the spin velocity is directed on the $xy$ plane as
\begin{align}
\gamma_{\mathrm{b}} (\omega,\alpha)
&=
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)}
{\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)} \right),
\label{eq:gamma-ang}
\end{align}
where the angle is measured in the counter-clockwise direction from the positive
$x$ Cartesian coordinate. We also define two special angles
\begin{align}
\gamma_{\mathrm{b \parallel}}(\omega,\alpha) &= \alpha, 
\label{eq:gamma-par} 
\\
\gamma_{\mathrm{b \perp}}(\omega,\alpha) &= \alpha \pm 90^{\circ}.
\label{eq:gamma-perp}
\end{align}
The first corresponds to the case when the spin velocity is directed, on the
$xy$ plane in the same direction of the polarization angle of the incoming beam;
the second one corresponds to the case when the spin velocity is directed
perpendicularly respect to the polarization angle of the incoming beam.

@@

Another possibility to analyze the spin velocity (Eq. \eqref{eq:vab}) is fixing
the velocity on the $xy$ plane along $x$ or $y$ Cartesian coordinate and then
define the magnitude of the spin velocity directed along the $\mathrm{a}$
direction as
\begin{align}
|\mathcal{V}^{\mathrm{a}}&(\omega,\alpha)| = \nonumber \\
&\sqrt { 
[\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)]^{2} +
[\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)]^{2} +
[\mathcal{V}^{\mathrm{az}}(\omega,\alpha)]^{2} .
},
\label{eq:vv-mag}
\end{align}
Then, the spin direction depends of the components of the previous equation and
so we define the spin orientation polar and azimuthal angles as
\begin{align}
\theta_{\mathrm{a}}  (\omega,\alpha)
=& 
\cos^{-1} \left( \frac{\mathcal{V}^{\mathrm{az}}(\omega,\alpha)}
{|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|} \right),
& 0 \leq &\theta \leq \pi, 
\label{eq:polar-ang}
\\
\varphi_{\mathrm{a}} (\omega,\alpha)
=& 
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)}
{\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)} \right),
& 0 \leq &\varphi \leq 2\pi.
\label{eq:azimuthal-ang} 
\end{align}
where $\theta_{\mathrm{a}}(\omega,\alpha)$ is measured from the positive to the
negative $z$ Cartesian coordinate and $\varphi_{\mathrm{a}}(\omega,\alpha)$ is
measured on the $xy$ plane in the counter-clockwise direction from the positive
$x$ Cartesian coordinate.

@@

Using the Eq. \eqref{eq:vs-mag}, we calculated the
$|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)|$ response and made the
analysis for the case when the spin is fixed in the $z$ direction, directed
perpendicularly to the surface of the \emph{up} and \emph{alt} structures. Also,
using the Eq. \eqref{eq:gamma-ang}, we determined the angle
$\gamma_{\mathrm{b}}(\omega,\alpha)$ where the spin-velocity is directed on the
surface of the each structure.
% 
For both cases, the most interesting case is that for which the spin is
perpendicular to the surface corresponding to $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$.

@@

@@

We first analyzed two energy ranges for the \emph{up} structure, the first for
an incoming energy beam from 0.0\,eV to 0.2\,eV which include the THz and the
Mid Infrared (MIR) radiation, where the absolute maximum of the

@@

values for which the response is maximized for the \emph{up} structure. In the

@@

from evaluate Eq. \eqref{eq:gamma-ang}, and in the bottom frames the panels we
present the corresponding components $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$
and $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$. Also we present two circled and

@@

parallel (Eq. \ref{eq:gamma-par}) and perpendicular (Eq. \ref{eq:gamma-perp})
and the arrows are directed to the value of the response corresponding to those

@@

and the response direction angle are collinear corresponding to

@@

For the \emph{alt} structure we analyzed the energy range for the incident beam
from 0.6\,eV to 1.0\,eV, corresponding to the NIR radiation, where the absolute
maximum of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response is
obtained.
% 
In Fig. \ref{fig:alt-3d-vsb} we present the
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ spectra for the \emph{alt}
structure.
% 
% From this figure we found that the zone where the absolute maximum response is
% held corresponds to a energy range from 0.90\,eV to 0.93\,eV and polarization
% angles $\alpha$ between $120^{\circ}$ and $150^{\circ}$. Also, a local maximum
% is obtained for the same polarization angles but for energies between 0.67\,eV
% and 0.75\,eV.
% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of ALT |V_{s^z}| & gamma  vs. alpha agle
% %%%%%%%%%%%%%%%%%
% 
From Figs. \ref{fig:alt-3d-vsb} and \ref{fig:alt-vaz-rag} we have that the
absolute maximum response is obtained for an incoming beam with polarization
angle $\alpha=145^{\circ}$ reaching a velocity of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 43.0$\,Km/s for the spin
polarized in the $\mathrm{z}$ direction and resulting in a velocity angle
$\gamma_{\mathrm{z}}(\omega,\alpha)=50^{\circ}$ on the first Cartesian Quadrant
of the $xy$ plane.
% 
Also, from the top frame of Fig. \ref{fig:alt-vaz-rag} we found that the
velocity angle has small variations being centered at $51.5^{\circ}$ and having
variations of $\pm 2^{\circ}$ for the polarization angle range $0^{\circ} \leq
\alpha \leq 180^{\circ}$.
% 
Again the circled box indicates the collinear angle (Eq.
\eqref{eq:gamma-par}) corresponding to
$\gamma_{\mathrm{z}\parallel}(\omega,\alpha) = 53.5^{\circ}$ corresponding a
value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 12.7$\,Km/s; the
blue square box indicates the perpendicular angles corresponding values
$\alpha=140^{\circ}$ and $\gamma_{\mathrm{z}\perp}(\omega,\alpha)=50^{\circ}$
with a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=43$\,Km/s.
% 
Again, for the cases in which the spin polarization is parallel to the surface
of the \emph{alt} structure was calculated but the plots are not presented here.
The absolute maxima for the case when the spin polarization is directed in the
$\mathrm{x}$ and $\mathrm{y}$ direction are obtained for an energy of the
incoming beam equal to 0.912\,eV and polarization angle $\alpha=145^{\circ}$
resulting in values of
$|\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)|=27.1$\,Km/s and
$|\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha)|=33.2$\,Km/s.
